---
output: github_document
bibliography: 'README_bibs.bib'
csl: 'apa-old-doi-prefix.csl'
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Travis build status](https://travis-ci.org/gederajeg/wordpairs.svg?branch=master)](https://travis-ci.org/gederajeg/wordpairs) [![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/gederajeg/wordpairs?branch=master&svg=true)](https://ci.appveyor.com/project/gederajeg/wordpairs) [![Coverage status](https://codecov.io/gh/gederajeg/wordpairs/branch/master/graph/badge.svg)](https://codecov.io/github/gederajeg/wordpairs?branch=master) 
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![DOI](https://img.shields.io/badge/doi-10.26180/5ba868cee0ef4-blue.svg?style=flat)](http://dx.doi.org/10.26180/5ba868cee0ef4)

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# wordpairs

The goal of wordpairs is to retrieve the occurrences of a pair of words in sentences. This is still under development and it is originally designed with sentence-based corpus of the Indonesian [Leipzig Corpora Collection](http://wortschatz.uni-leipzig.de/en/download) as the input. If each line of your corpus text does not correspond to one sentence as in the Leipzig Corpora (e.g., consisting of multiple sentences or split sentences between multiple lines), few tweaking is needed (read further below after the **Example** section).

## Installation

You can install the development version of wordpairs from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gederajeg/wordpairs")
```
## Example

Here is an example to search for the occurrences of Indonesian words with *me- -kan* confix, which indicate (di)transitive verbs, and the preposition *kepada* 'to(wards) sb.'. The package comes with a random sample of 25,000 sentences from one corpus file of the Indonesian Leipzig Corpora (i.e. the `"ind_news_2008_300K-sentences.txt"`).

```{r example}
library(wordpairs)
word_1 <- "\\bmen[a-z]{3,}kan\\b"
word_2 <- "\\bkepada\\b"
corpus <- my_leipzig_sample
m <- word_pairs(corpus,
                word_1 = word_1,
                word_2 = word_2,
                min_intervening = 0L,
                max_intervening = 3L)
```

Next, we can inspect snippets of the output as follows.

```{r output-inspect}
str(m)
```

The `pattern` consists of the extracted patterns for the co-occurrences of `word_1` and `word_2`. Note that `word_1` always precedes `word_2`, if they do co-occur in a sentence. To reverse the co-occurrence sequence, reverse the input for `word_1` with `word_2`, and *vice versa*.

The `pattern_tagged` is the tagged version of elements in `pattern`. The tags enclose `word_1` and `word_2`, but not the intervening strings.

The `matches` shows the occurrences of the `pattern` in the full sentential contexts in which they are found.

Next, we can create a frequency table for the detected co-occurrence patterns, using the [dplyr](https://dplyr.tidyverse.org) package from the [tidyverse](https://www.tidyverse.org).

```{r freq-pattern, warning = FALSE, message = FALSE}
# generate frequency table for the patterns using `dplyr` package
library(dplyr)
freq_tb <- 
  tibble(pattern = m$pattern_tagged) %>% 
  count(pattern, sort = TRUE)
head(freq_tb)
```

## Tweaking non-sentence corpus input

As mentioned above, non-sentence corpus needs to be preprocessed before using it as input for `word_pairs()`. The package includes an example of typical input text where each line does not correspond to one sentence, or the sentence elements got split into two or more lines.

```{r bola-corpus}
wordpairs::bola_corpus_text
```

We can see, for instance, that the beginning of line two contains elements (i.e. the strings `"dan Jerman."`) of sentence in line one. The first step to handle this is to collapse elements of this character vector into one long character vector.

```{r collapse-bola}
bola_corpus <- paste(wordpairs::bola_corpus_text, collapse = " ")
```

Next, we can use the `tokenize_sentences()` function from the [tokenizers](https://cran.r-project.org/web/packages/tokenizers/index.html) [@mullen_tokenizers] package to split the collapsed string into character vector whose elements correspond to one sentence. You first need to install the tokenizers package in R.

```{r tokenize-bola}
# install tokenizers if you have not done it.
# install.packages("tokenizers")

bola_corpus <- tokenizers::tokenize_sentences(bola_corpus, simplify = TRUE)
bola_corpus
```

Now, `bola_corpus` vector can be used as input for the `corpus` argument of `word_pairs()`.


## Citation

To cite wordpairs, please use:

- Rajeg, Gede Primahadi Wijaya. (2018). *wordpairs*: An R package to retrieve word pair in sentences. Retrieved from: https://gederajeg.github.io/wordpairs/

## References

