---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Travis build status](https://travis-ci.org/gederajeg/wordpairs.svg?branch=master)](https://travis-ci.org/gederajeg/wordpairs) [![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/gederajeg/wordpairs?branch=master&svg=true)](https://ci.appveyor.com/project/gederajeg/wordpairs) [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.1422866.svg)](https://doi.org/10.5281/zenodo.1422866)

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# wordpairs

The goal of wordpairs is to retrieve the occurrences of a pair of words in sentences. This is still under development and it is designed with sentence-based corpus of the Indonesian [Leipzig Corpora Collection](http://wortschatz.uni-leipzig.de/en/download) as the input. Further testing with different corpus-input is needed.

## Installation

You can install the development version of wordpairs from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gederajeg/wordpairs")
```
## Example

Here is an example to search for the occurrences of Indonesian words with *me- -kan* confix, which indicate (di)transitive verbs, and the preposition *kepada* 'to(wards) sb.'. The package comes with a random sample of 25,000 sentences from one corpus file of the Indonesian Leipzig Corpora (i.e. the `"ind_news_2008_300K-sentences.txt"`).

```{r example}
library(wordpairs)
word_1 <- "\\bmen[a-z]{3,}kan\\b"
word_2 <- "\\bkepada\\b"
corpus <- my_leipzig_sample
m <- word_pairs(corpus,
                word_1 = word_1,
                word_2 = word_2,
                min_intervening = 0L,
                max_intervening = 3L)
```

Next, we can inspect snippets of the output as follows.

```{r output-inspect}
str(m)
```

The `pattern` consists of the extracted patterns for the co-occurrences of `word_1` and `word_2`. Note that `word_1` always precedes `word_2`, if they do co-occur in a sentence. To reverse the co-occurrence sequence, reverse the input for `word_1` with `word_2`, and *vice versa*.

The `pattern_tagged` is the tagged version of elements in `pattern`. The tags enclose `word_1` and `word_2`, but not the intervening strings.

The `matches` shows the occurrences of the `pattern` in the full sentential contexts in which they are found.

Next, we can create a frequency table for the detected co-occurrence patterns, using the [dplyr](https://dplyr.tidyverse.org) package from the [tidyverse](https://www.tidyverse.org).

```{r freq-pattern, warning = FALSE, message = FALSE}
# generate frequency table for the patterns using `dplyr` package
library(dplyr)
freq_tb <- 
  tibble(pattern = m$pattern_tagged) %>% 
  count(pattern, sort = TRUE)
head(freq_tb)
```


## Citation

To cite wordpairs, please use:

- Rajeg, Gede Primahadi Wijaya. (2018). *wordpairs*: An R package to retrieve word pair in sentences. Retrieved from: https://doi.org/10.5281/zenodo.1422866
